Students' Alcohol Consumption Impacts on Academic Results on the Example of a Secondary Scool Maths Class in Portugal

### 2016-10-15 knit_MSproject.Rmd
small changes to read.csv

## 2. Dataset Description and Descriptive Statistics 
```{r a, include=FALSE}
########################## Read csv file########################
sm <- read.csv("/Users/deasysibarani/Desktop/Math_Statistics_Foundations/Group Project/student/student-mat.csv", sep=';') 
# academic performance is measured by the average of exam scores
sm[, "Score"] <- (sm[, "G1"] + sm[, "G2"] + sm[, "G3"])/3

@@

# 1. father or mother job is teacher = 1
sm$f_or_mteach <- 0
sm[,"f_or_mteach"] <- as.character(sm[,"f_or_mteach"])
for (j in 1:nrow(sm)) {

@@

# 2. father or mother earns university degree = 1 
sm$f_or_medu <- 0
sm[,"f_or_medu"] <- as.character(sm[,"f_or_medu"])
for (j in 1:nrow(sm)) {

>>>>

## 2. Dataset Description and Descriptive Statistics 
```{r a, include=FALSE}
########################## Read csv file########################
sm <- read.csv("student-mat.csv", sep=';') 
# academic performance is measured by the average of exam scores
sm[, "Score"] <- (sm[, "G1"] + sm[, "G2"] + sm[, "G3"])/3

@@

# 1. father or mother job is teacher = 1

sm$f_or_mteach <- 0
sm[,"f_or_mteach"] <- as.character(sm[,"f_or_mteach"])
for (j in 1:nrow(sm)) {

@@

# 2. father or mother earns university degree = 1

sm$f_or_medu <- 0
sm[,"f_or_medu"] <- as.character(sm[,"f_or_medu"])
for (j in 1:nrow(sm)) {
